\documentclass{article}
\usepackage[utf8]{inputenc}

\newenvironment{tightcenter}{%
  \setlength\topsep{0pt}
  \setlength\parskip{0pt}
  \begin{center}
}{%
  \end{center}
}
\pagenumbering{gobble}

\usepackage[left=2cm, right=2cm, top=1cm, bottom=1cm]{geometry}

\usepackage{titlesec}
\usepackage{enumitem}

\titleformat*{\section}{\fontsize{11}{0}\selectfont}
\titlespacing*{\section}{0pt}{2pt}{0pt}
\titleformat*{\subsection}{\fontsize{8}{0}\selectfont}
\titlespacing*{\subsection}{0pt}{0pt}{0pt}
\setlist[itemize]{leftmargin=*}


\begin{document}

\begin{tightcenter}
\begin{Large}Niles Christensen\\
\end{Large}
\begin{small}
5434 Ellsworth Ave., Pittsburgh, PA, 15232\\
650-714-3983\\
nilesnchristensen@gmail.com
\end{small}
\end{tightcenter}

\noindent
\large{\textbf{Experience}}

\section*{\textbf{Research Assistant For Prof.\ Vondrick, Columbia University \hfill	Spring 2019}}
\begin{itemize}[noitemsep]
    \item Adapated an existing optical flow pyramid network to a video colorization task.
    \item Made changes allowing for greatly simplified structure tuning and massively improved readability.
\end{itemize}

\section*{\textbf{Project with Prof.\ Drori, Columbia University \hfill Spring 2019}}
\begin{itemize}[noitemsep]
  \item Built a class project with 2 classmates that leverage tree-structured debate data to retrain existing seq2seq models to respond to a debate prompt.
  \item Worked closely with Prof.\ Drori afterward to further refine results and compare results to human debaters through Mechanical Turk.
\end{itemize}

\section*{\textbf{Teaching Assistant, Columbia University \hfill	Spring 2017 -- Spring 2019 }}
\begin{itemize}
    \item Fundamentals of Computer Science, held weekly seminars for students and graded exams.
\end{itemize}

%\section*{\textbf{Research Assistant For Prof.\ Rubenstein, Columbia University \hfill	Spring 2017 -- Spring 2018}}
%\begin{itemize}[noitemsep]
%    \item Implemented user interface with Django and React to allocate bandwidth caps on a specialized router
%    \item Investigated using neural networks to determine general content type of encrypted packets
%\end{itemize}

\section*{\textbf{Software Engineering Intern, Loon, Mountain View, California \hfill Summers 2018, 2019}}
\subsection*{Google X}
\begin{itemize}[noitemsep]
    \item Created automated logging systems to gather data on links in Loon’s balloon internet system.
    \item Made improvements to Loon's altitude- and wind-based balloon steering system.
    \item Created visualizations to better understand the outcomes of complex simulations.
    \item Added infrastructure to allow for black-box optimization of fleet performance in simulations.
\end{itemize}

\section*{\textbf{Software Engineering Intern, Google, Mountain View, California \hfill Summer 2017}}
\subsection*{Adwords Group}
\begin{itemize}
    \item Created an interface for AdWords critical to the process of signing up large companies and securing large contracts. Worked closely with Billing and User Management teams.
\end{itemize}


\section*{\textbf{Intern, Brain of Things, Redwood City, California	\hfill Summer 2016}}
\subsection*{Brain of Things is a start-up developing a fully integrated home automation solution based on artificial intelligence. }
\begin{itemize}[noitemsep]
    \item Implemented features to adjust the home's lighting colors to reflect the color palette of an image sent via text message to the house 
    \item Developed an alarm feature that used hardware installed in the house to wake up users at a time of their choosing through curtains opening and lights turning on
    \item Cloud-based and local features were implemented in Python and Javascript on Unix
\end{itemize}

\section*{\textbf{Developer and Advisor, Socialsquare, Copenhagen, Denmark \hfill Fall 2014-Spring 2015}}
\subsection*{Socialsquare is a consulting company working with clients to create custom open-source tools and solutions}
\begin{itemize}[noitemsep]
    \item Created a Django website to connect runners and sponsors for charity events, and automatically charge sponsors based on distances run by the runners
    \item Designed a low-cost system to track the location of handball players on a court to allow for better analytics and commentary on games in real time
\end{itemize}

\section*{\textbf{Internships \& Tutoring \hfill Fall 2011- Summer 2014
}}
\begin{itemize}[noitemsep]
    \item Intern, Genia Chip; Wrote Bash programs to test existing hardware. Programmed and assembled boards to support the Genia chip and allow for further development
    \item Tutor: Tutored local students in Java, Python, math and sciences (both paid and volunteer)
    \item Teaching Assistant, Menlo School, Advanced Topics in Computer Science
\end{itemize}

\noindent
{\large\textbf{Education}}
\begin{itemize}[noitemsep]
    \item Columbia University, New York, NY -- May 2019, GPA 3.94/4.0, CS Major (Intelligent Systems)
    \item Menlo High School, Atherton, California -- GPA 4.1/4.0
\end{itemize}

\noindent
{\large\textbf{Skills}}
\begin{itemize}[noitemsep]
    \item Java, Python, Latex, Go, Django, Agile Development, Some Circuitry
    \item Proficient in French and Danish, some Spanish
\end{itemize}
\noindent
{\large\textbf{Awards \& Leadership}}
\begin{itemize}[noitemsep]
    \item Columbia's Deans List 6 terms
    \item Member of CU Swing Dancing Club Executive Board

\end{itemize}
\end{document}
