%% start of file `template.tex'.
%% Copyright 2006-2013 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[11pt,a4paper,sans]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')

% moderncv themes
\moderncvstyle{casual}                             % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue}                               % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
%\renewcommand{\familydefault}{\sfdefault}         % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
%\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page

% character encoding
\usepackage[utf8]{inputenc}                       % if you are not using xelatex ou lualatex, replace by the encoding you are using
%\usepackage{CJKutf8}                              % if you need to use CJK to typeset your resume in Chinese, Japanese or Korean

% adjust the page margins
\usepackage[scale=0.75]{geometry}
%\setlength{\hintscolumnwidth}{3cm}                % if you want to change the width of the column with the dates
%\setlength{\makecvtitlenamewidth}{10cm}           % for the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...

% personal data
\name{Niles}{Christensen}
% \title{Resumé title}                               % optional, remove / comment the line if not wanted
\address{5434 Ellworth Ave}{Pittsburgh}{PA, 15232}
\phone[mobile]{+1~(650)~714~3983}                   % optional, remove / comment the line if not wanted
\email{nilesnchristensen@gmail.com}                               % optional, remove / comment the line if not wanted

% to show numerical labels in the bibliography (default is to show no labels); only useful if you make citations in your resume
%\makeatletter
%\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}
%\makeatother
%\renewcommand*{\bibliographyitemlabel}{[\arabic{enumiv}]}% CONSIDER REPLACING THE ABOVE BY THIS

% bibliography with mutiple entries
%\usepackage{multibib}
%\newcites{book,misc}{{Books},{Others}}
%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
%-----       letter       ---------------------------------------------------------
% recipient data
\recipient{Loon Steering Team}{100 Mayfield Ave.\\Mountain View\\CA}
\date{November 26, 2019}
\opening{To whom it may concern,}
\closing{Thank you for your consideration,}
\makelettertitle
I'm writing this letter to ask to be considered as an intern for the Loon steering team for this Summer.

I believe that I am a strong candidate for this position. I completed my undergraduate studies in
Computer Science with a focus on Intelligent Systems at Columbia this past Spring, and am
currently enrolled in Carnegie Mellon's Master's of Machine Learning program. In addition to
my coursework, I have firsthand experience on a number of different projects, such that I
am comfortable both taking the lead on a new project and efficiently onboarding to an existing
one. As such, I'll be able to hit the ground running, no matter the task. Furthermore, my coursework
in machine learning has given me the skillset needed to handle the large amounts of data and open-ended
problems that Loon's steering team constantly encounters.

Furthermore, I have interned at Loon twice, including when it was still a part of X. During this time,
I have made several significant contributions, including a system to improve stashing behaviors for
balloons that are not currently serving any specific area, and a system to provide automatic telemetry on
links between balloons, something that was not previously available. Thanks to this, I am already familiar
with large portions of Loon's tech stack and architecture, and would be able to start contribting immediately.

Finally, working at Loon has given me an appreciation for the importance of its mission. By spreading internet
to areas that wouldn't normally have it, either due to disaster or otherwise, Loon connects people and
allows for economic equity and opportunity in ways that wouldn't have been possible otherwise. Loon's radically
different approach to a huge problem can and has changed people's lives for the better, and it's a mission I'm
proud to have been part of, and hope to contribute to further.

\makeletterclosing

\end{document}


%% end of file `template.tex'.
